MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-08-02 darmstadt_gscl_2013/article_twitter_normalization.tex
section "Analysis of unknwon words" completed (init version)

  This article gives an overview of existing approaches to the problem
  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
  language texts. These approaches are classified with regard to the
  size of text spans and knowledge inference mechanisms which they
  rely on in their work. Additionally to that, we conduct quantitative
  and qualitative analyses of unknown words in German Twitter
  messages, in order to see how relevant the OOV and text
  normalization problems are for this particular kind of micro-texts
  and what the characteristics of these OOVs are. In a concluding
  step, we present a set of ad-hoc techniques which are supposed to
  tackle some of the most prominent disturbing effects found during
  these analyses and show how this set of techniques helps us lower
  the average rate of out-of-vocabulary tokens in Twitter messages and
  how this lower OOV-rate helps improve the quality of automatic
  part-of-speech tagging.

@@

Though both divisions seem to be justified to some extent, it is
difficult to determine using them whether an NTN approach that detects
and restores incorrectly spelled words on the basis of phonetical
\textit{n}-gram statistics should fall into \textit{n}-gram based,
probabilistic, spell checking or speech recognition class.

The reason for this confusion is the fact that the above
classifications both rely on several independent criteria at the same
time though each of these criteria characterizes an NTN system from a
different point of view. As a consequence, unambiguous assignment of
an NTN approach to one particular class often becomes impossible. In
order to avoid this, we instead suggest using separate classifications
for each criterion which might characterize an NTN technique.

One of such criteria which in our opinion would be worth a separate
classification is \emph{segmentation level} which is used
\begin{inparaenum}[\itshape a\upshape)]
\item to infer in-vocabulary (IV) equivalents for OOV
  tokens\label{candidate:inferring} and
\item to choose the most probable variant\label{candidate:selection}
  among multiple possible suggestions\footnote{For the cases, when
    segments of different lengths are used for tasks
    \ref{candidate:inferring} and \ref{candidate:selection}, we note
    it explicitly in our classification on which segmentation length
    each of these subtasks relies.}.
\end{inparaenum} For this criterion, we propose division into the following
classes:
\begin{enumerate}
  \item graphematic\footnote{Depending on whether phonetical
    information is involved or not at this level, this class could be
    further divided into a phonographematic and purely graphematic
    subclasses.};
  \item lexical;
  \item phrasal.
\end{enumerate}
Each broader level of this hierarchy is supposed to either incorporate
or ignore information provided by its narrower subsegments. In this
way, we only need to mention one (the broadest) hierarchical class for
the cases when multiple segmentation levels are involved by some
techniques.

@@

The earlier works on NTN commonly relied on either purely graphematic
or phonographematic levels of segmentation for deriving normalization
variants of incorrectly spelled words. To purely graphematic systems
belong methods suggested Brill and Moore (\cite{brill}), Sproat et
al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
phonographematic approaches one could regard works done by Toutanova
and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
Cook and Stevenson (\cite{cook}) etc. With regard to the type of
information inference, practically all of these methods were
supervised with the exception of Cook and Stevenson (\cite{cook}) who
claimed to uns an unsupervised technique.

@@

In order to estimate the percentage of unknown words in Twitter
messages, we randomly selected 10,000 tweets from a previously
collected corpus, split them into sentences and tokenized using social
media-aware tokenizer by Christopher Potts
\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
After skipping all words which did not contain any alphabetic
character in them or consisted only of a single letter, we obtained a
list of 129,146 tokens. As reference systems for dictionary lookup we
used open source spell checking program
\texttt{hunspell}\footnote{Ispell Version 3.2.06 (Hunspell Version
  1.3.2); dictionary de\_DE.} and publicly available part-of-speech
tagger \texttt{TreeTagger}\footnote{Version 3.2 with German parameter
  file UTF-8.} (Schmid, \cite{schmid}).

@@

Here once again the question of classification arose. This time with
regard to the reasons, why different tokens could have been omitted
from corresponding applications' dictionaries. In this respect,
division into following groups seemed to be appropriate for us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for the inclusion in
    this type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to
    impossibility to fully cover these classes;\label{dict}
  \item \textbf{Unintended sloppiness of users' input}. In the scope
    of this second group, we considered unintended typos;\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language texts but were perfectly valid
    terms in the domain of web discourse and Twitter communication in
    particular.\label{style}
\end{enumerate}

@@

We subdivided group \ref{dict} into the following subgroups:
\begin{enumerate}
\item regular German words, e.g. \textit{aufm},
  \textit{losziehen};\label{regular}
\item compounds, e.g.  \textit{Altwein},
  \textit{Amtsapothekerin};\label{compound}
\item abbreviations, e.g. \textit{NBG}, \textit{OL};\label{abbr}
\item interjections, e.g.  \textit{aja}, \textit{haha};\label{inj}
\item named entities, with subclasses:\label{ne}
  \begin{enumerate}
  \item persons, e.g.  \textit{Ahmadinedschad}, \textit{Schweiger};
  \item geographic locations, e.g.  \textit{Biel}, \textit{Limmat};
  \item companies, e.g. \textit{Apple}, \textit{Facebook};
  \item product names, e.g. \textit{iPhone}, \textit{MacBook};
  \end{enumerate}
\item neologisms, with subclasses:\label{neolog}
  \begin{enumerate}
    \item newly coined German terms, e.g. \textit{entfolgen},
      \textit{gegoogelt};\label{new}
    \item loanwords, e.g. \textit{Community},
      \textit{Stream};\label{loan}
  \end{enumerate}
\item and, finally, foreign words like \textit{is} or \textit{now}
  which in contrast to \ref{loan} were not mentioned in any existing
  German lexicons and did not comply with inflectional rules of German
  grammar.\label{fw}
\end{enumerate}
Though this division is admittedly arbitrarily to a certain degree and
involves different linguistic criteria simultaneously, the underlying
notion for it is simple. Valid words could have been omitted from an
MRD either due to the limitation of developers' capacities (group
\ref{regular}), active word formation or lexical productivity of the
language (groups \ref{compound} through \ref{new}) or also due to
language's openness to foreign language systems (groups \ref{loan} and
\ref{fw}).

In Table \ref{table:mrd}, percentage figures for each of the above
subgroups are shown. We have considered OOV-distribution for both
\texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
estimated the percentage of a particular subclass with regard to the
total number of occurrences of OOV-tokens (column ``\totaloov{}'') as
well as with regard to their percentage rate in the list of only
unique OOVs (column ``\uniqoov{}''), i.e. disregarding their
frequencies.

dict           3.49
compound       4.55
abbr           3.44
inj            4.29
ne:person      3.47
ne:geo         1.88
ne:company     3.01
ne:product     3.23
neologism      2.38
loan           2.87
fw             10.91

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
    person names & 4.73 & 6.41 & 2.32 & 3.47\\
    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
    company names & 2.27 & 2.84 & 4.35 & 3.01\\
    product names & 2.13 & 2.57 & 2.45 & 3.23\\
    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to class \ref{dict}, we subdivided the class ``Unintended
sloppiness of users' input'' into the following subgroups:
\begin{enumerate}
  \item insertion;
  \item deletion;
  \item substitution;
\end{enumerate}
according to the kind of operation which led to a particular spelling
mistake. In cases when multiple different operations were involved
simultaneously, we explicitly marked each of these operations in our
data. You can see the statistics on distribution of these subgroups in
Table \ref{table:spell}.

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``unintended sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertion & 0.49 & 1 & 0.18 & 0.34 \\
    deletion & 8.44 & 6.38 & 6.52 & 5.27 \\
    substitution & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

As it is clear from the table, deletions are by far the most common
type of spelling mistakes. This results on the one hand from
deliberate or unintended omissions of characters made by users but an
even more common source of these ill-formed words was automatic
truncation of words at the end of tweets made by Twitter service
itself. \footnote{As is generally known, Twitter imposes a strong
  restriction on the length of posted messages which can be no longer
  than 140 characters. Upon exceeding this length, tweets get
  automatically truncated to maximal allowed length.}

\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Stylistic specifics of text genre''}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
    links & 2.43 & 0.4 & 4.89 & 6.07\\
    smileys & 2 & 0.73 & 6.88 & 1.2\\
    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

@@

This article provided an overview of exisiting approaches to noisy
text normalization task. Additionally, all mentioned methods were
classified on the basis of two independent criteria. In section
\ref{error:analysis}, we performed qulitative and quantitive analyses
of out-of-vocabulary words in German tweets and suggested a set of
ad-hoc techniques for mitigating their potential negative influence on
natural language processing. This procedure allowed us to reduce the
total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
\texttt{TreeTagger}.

Nevertheless, we should honestly admit that our system still has
potential for development and research, since it mainly addresses only
one of three main groups of OOV tokens. Future directions should
certainly include a more thorough tackling of unintentional spelling
mistakes and especially their most prominent types -- deletions and
substitutions.

Furthemore, a better evalution technique as well as comparison with
other systems are needed for our normalization procedure. On the one
hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
Jones and Galliers, \cite{sparck}) which means that we not only have
to show how the rate of OOV words goes down but much more how this
lower OOV rate affects the work of the whole NLP system. On the other
hand, we need to assess the quality of our procedure's work on the
basis of metrics used by other researchers.

One possible estimation criterion which was used by Aw et
al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
score (Papineni et al., \cite{papineni}). Another possibility would be
to use the Word (WER) and Sentence Error Rates (SER) as suggested by
Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
already encountered here is that both metrics highly rely on a
subjective notion of the look of a ``normalized'' message. While the
BLEU score could be an approriate criterion for normalization of
messages like ``i luv ma mather and wd do evrythin 4 her'' which in
fact looks like as if it were not English. But such highly distorted
tweets are rather atypical for German. In this regard, WER and SER
could be considered as more appropriate measurement criteria. But
these metrics once again are rather dealing with spelling mistakes and
would highly depend on whether one, for example, would consider the
hash sign in a hashtag as an error.

>>>>

  This article gives an overview of existing approaches to the problem
  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
  language texts. These approaches are classified with regard to the
  size of text spans and knowledge inference mechanisms which they
  rely on in their work. Additionally to that, we conduct quantitative
  and qualitative analyses of unknown words in German Twitter
  messages, in order to see how relevant the OOV and text
  normalization problems are for this particular kind of micro-texts
  and what the characteristics of these OOVs are. In a concluding
  step, we present a set of ad-hoc techniques which are supposed to
  tackle some of the most prominent disturbing effects found during
  these analyses and show how this set of techniques helps us lower
  the average rate of out-of-vocabulary tokens in Twitter messages and
  how this lower OOV-rate in turn helps improve the quality of
  automatic part-of-speech tagging.

@@

Though both divisions seem to be justified to some extent, it is
difficult to determine using them whether an NTN approach that detects
and restores incorrectly spelled words on the basis of phonetical
\textit{n}-gram statistics should fall into the \textit{n}-gram based,
probabilistic, spell checking or speech recognition class.

The reason for this confusion is the fact that the above
classifications both rely on several independent criteria at the same
time, though each of these criteria characterizes an NTN system from a
different point of view. As a consequence, unambiguous assignment of
an NTN approach to one particular class often becomes impossible. In
order to avoid this, we instead suggest using separate classifications
for each type of involved criteria which might characterize an NTN
technique.

One of such criteria which in our opinion would be worth a separate
classification is \emph{segmentation level} that is used
\begin{inparaenum}[\itshape a\upshape)]
\item to infer in-vocabulary (IV) equivalents for OOV
  tokens\label{candidate:inferring} and
\item to choose the most probable variant\label{candidate:selection}
  among multiple possible suggestions\footnote{For the cases, when
    segments of different lengths are used for tasks
    \ref{candidate:inferring} and \ref{candidate:selection}, we note
    it explicitly in our classification on which segmentation length
    each of these subtasks relies.}.
\end{inparaenum} For this criterion, we propose division into the following
classes:
\begin{enumerate}
  \item graphematic\footnote{Depending on whether phonetical
    information is involved or not at this level, this class could be
    further divided into a phonographematic and purely graphematic
    subclasses.};
  \item lexical;
  \item phrasal.
\end{enumerate}
Each broader level of this hierarchy is supposed to either incorporate
or ignore information provided by its narrower subsegments. In this
way, we only need to mention one (the broadest) hierarchical class for
the cases when multiple segmentation levels are involved by some
techniques.

@@

The earlier works on NTN commonly relied on either purely graphematic
or phonographematic levels of segmentation for deriving normalization
variants of incorrectly spelled words. To purely graphematic systems
belong methods suggested by Brill and Moore (\cite{brill}), Sproat et
al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
phonographematic approaches one could regard works done by Toutanova
and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
Cook and Stevenson (\cite{cook}) etc. With regard to the type of
information inference, practically all of these methods were
supervised with the exception of Cook and Stevenson (\cite{cook}) who
claimed to use an unsupervised technique.

@@

In order to estimate the percentage of unknown words in Twitter
messages, we randomly selected 10,000 tweets from a previously
collected corpus, split them into sentences and tokenized using social
media-aware tokenizer by Christopher Potts
\footnote{\url{http://sentiment.christopherpotts.net/code-data/happyfuntokenizing.py}}.
After skipping all words which did not contain any alphabetic
characters or consisted only of a single letter, we obtained a list of
129,146 tokens. As reference systems for dictionary lookup we used
open source spell checking program \texttt{hunspell}\footnote{Ispell
  Version 3.2.06 (Hunspell Version 1.3.2); dictionary de\_DE.} and
publicly available part-of-speech tagger
\texttt{TreeTagger}\footnote{Version 3.2 with German parameter file
  UTF-8.} (Schmid, \cite{schmid}).

@@

Here once again the question of classification arose. This time with
regard to the reasons, why different tokens could have been omitted
from corresponding applications' dictionaries. In this respect,
division into following groups seemed to us to be appropriate:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. Among this group, we counted words of basic vocabulary
    which did not get into applications' MRD either because they
    supposedly were rare or because they did not exist at the time
    when dictionaries were created. Another reason for the inclusion
    in this type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are often omitted from MRDs due to
    the impossibility to fully cover these classes;\label{dict}
  \item \textbf{Sloppiness of users' input}. In the scope of this
    second group, we considered incorrect spellings of words
    encountered in text;\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language but were perfectly valid terms
    in the domain of web discourse or more specifically in Twitter
    communication.\label{style}
\end{enumerate}

@@

We subdivided the class \ref{dict} into the following subclasses:
\begin{enumerate}
\item regular German words, e.g. \textit{aufm},
  \textit{losziehen};\label{regular}
\item compounds, e.g.  \textit{Altwein},
  \textit{Amtsapothekerin};\label{compound}
\item abbreviations, e.g. \textit{NBG}, \textit{OL};\label{abbr}
\item interjections, e.g.  \textit{aja}, \textit{haha};\label{inj}
\item named entities, with subclasses:\label{ne}
  \begin{enumerate}
  \item persons, e.g.  \textit{Ahmadinedschad}, \textit{Schweiger};
  \item geographic locations, e.g.  \textit{Biel}, \textit{Limmat};
  \item companies, e.g. \textit{Apple}, \textit{Facebook};
  \item product names, e.g. \textit{iPhone}, \textit{MacBook};
  \end{enumerate}
\item neologisms, with subclasses:\label{neolog}
  \begin{enumerate}
    \item newly coined German terms, e.g. \textit{entfolgen},
      \textit{gegoogelt};\label{new}
    \item loanwords, e.g. \textit{Community},
      \textit{Stream};\label{loan}
  \end{enumerate}
\item and, finally, foreign words like \textit{is} or \textit{now}
  which in contrast to \ref{loan} were not mentioned in any existing
  German lexica and did not comply with inflectional rules of German
  grammar.\label{fw}
\end{enumerate}
Though this division is admittedly arbitrarily to a certain degree and
also has the disadvantage of simultaneously involving different
linguistic criteria, the underlying notion here was simple -- valid
words could have been omitted from an MRD either due to the
limitations of developers' capacities (group \ref{regular}), active
word formation processes or lexical productivity of the language
itself (groups \ref{compound} through \ref{new}) or also due to
language's openness to foreign language systems (groups \ref{loan} and
\ref{fw}).

In Table \ref{table:mrd}, percentage figures for each of the above
subgroups are shown. We have considered OOV-distributions for both
\texttt{hunspell} and \texttt{TreeTagger}. For each of them, we
estimated the percentage of a particular subclass with regard to the
total number of occurrences of OOV-tokens (column ``\totaloov{}'') as
well as with regard to their percentage rate in the list of only
unique OOVs disregarding their frequencies (column ``\uniqoov{}'').
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Objective limitedness of MRD''\label{table:mrd}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    regular German words & 7.82 & 8.78 & 2.8 & 3.49\\
    compounds & 1.21 & 2.42 & 2.51 & 4.55\\
    abbreviations & 3.98 & 4.77 & 3.27 & 3.44\\
    interjections & 5.95 & 4.54 & 5.58 & 4.29\\
    person names & 4.73 & 6.41 & 2.32 & 3.47\\
    geographic locations & 1.5 & 2.53 & 1.16 & 1.88\\
    company names & 2.27 & 2.84 & 4.35 & 3.01\\
    product names & 2.13 & 2.57 & 2.45 & 3.23\\
    newly coined terms & 1.35 & 1.31 & 3.33 & 2.38\\
    loanwords & 3.68 & 4.03 & 3.29 & 2.87\\
    foreign words & 11.5 & 13.76 &  9.57 & 10.91\\\hline
    {\bfseries total} & 46.12 & 53.96 & 40.63 & 43.52\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

Similarly to the class \ref{dict}, we subdivided the group
``Sloppiness of users' input'' into the following subgroups:
\begin{enumerate}
  \item insertions, e.g. \textit{dennen} instead of \textit{denen};
  \item deletions, e.g. \textit{scho} instead of \textit{schon};
  \item substitutions, e.g. \textit{fur} instead of \textit{f\"ur};
\end{enumerate}
according to the type of operation which led to a particular spelling
mistake. In cases when multiple different operations were involved
simultaneously, we explicitly marked each of these operations in our
data. Statistical distribution of these subclasses is shown in Table
\ref{table:spell}.
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Sloppiness of users' input''\label{table:spell}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    insertions & 0.49 & 1 & 0.18 & 0.34 \\
    deletions & 8.44 & 6.38 & 6.52 & 5.27 \\
    substitutions & 2.17 & 3.37 & 1.11 & 1.2 \\\hline
    {\bfseries total} & 11.1 & 10.75 & 7.81 & 6.81\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

As is clear from the table, deletions are by far the most common type
of misspellings. The reasons for that are on the one hand either
relatively frequent omissions of characters made by user or even more
often automatic truncations of too long messages which were performed
by Twitter service itself.\footnote{As is generally known, Twitter
  imposes a strong restriction on the length of posted messages which
  can be no longer than 140 characters. Upon exceeding this length,
  tweets get automatically truncated to the maximal allowed length.}

Finally, the third group -- ``Stylistic specifics of text genre'' --
was subdivided into the subgroups:
\begin{enumerate}
  \item hashtags, e.g. \textit{\#Kleinanzeigen};
  \item @-tokens, e.g. \textit{@ZDFonline};
  \item links, e.g. \textit{http://t.co};
  \item smileys, e.g. \textit{:-P};
  \item slang, e.g. \textit{OMG}.
\end{enumerate}
according to the lexical or syntactic class which these tokens
belonged to. Apart from lexical expressions pertaining to the genre of
Internet-based communication, we also marked as \textit{slang}
spelling variants of standard language words which could be regarded
as their corresponding colloquial equivalents. As such equivalents, we
considred spellings like \textit{ned} instead of \textit{nicht} or
\textit{grad} instead of \textit{gerade}. These cases were marked by
us both as misspellings and as slang. A detailed statistics on the
above subgroups of class 3 is shown in Table \ref{table:style}:
\begin{table}
  \caption{Distribution of OOV words belonging to the class
    ``Stylistic specifics of text genre''\label{table:style}}
  \begin{tabular}{p{0.4\textwidth}*{4}{>{\centering\arraybackslash}p{0.15\textwidth}}}
    \hline\noalign{\smallskip}
    \multirow{2}{*}{OOV subclass} & %
    \multicolumn{2}{c}{\texttt{hunspell}} & %
    \multicolumn{2}{c}{\texttt{TreeTagger}}\\
    & \totaloov{} & \uniqoov{} & \totaloov{} & \uniqoov{}\\
    \noalign{\smallskip} \hline
    hashtags & 7.35 & 6.18 & 13.06 & 10.59\\
    @-tokens & 13.02 & 20.23 & 16.19 & 21.91\\
    links & 2.43 & 0.4 & 4.89 & 6.07\\
    smileys & 2 & 0.73 & 6.88 & 1.2\\
    slang & 16.22 & 5.27 & 6.94 & 4.77\\\hline
    {\bfseries total} & 41.02 & 32.81 & 47.96 & 44.54\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

A striking outlier of 16.22~\% for slang in column 1 of the table is
due to the fact that the word ``RT'' which occurred 1,235 and was by
far the most frequent OOV in our data was recognized as
out-of-vocabulary by \texttt{hunspell} but not recognized as such by
\texttt{TreeTagger}.

This knowledge about composition of unknown and ill-formed words
should now help us select or devise techniques for recognizing and
correcting such tokens in cases where it is needed. These procedures
are described in the next Section of the article.

@@

%% This article provided an overview of exisiting approaches to noisy
%% text normalization task. Additionally, all mentioned methods were
%% classified on the basis of two independent criteria. In section
%% \ref{error:analysis}, we performed qulitative and quantitive analyses
%% of out-of-vocabulary words in German tweets and suggested a set of
%% ad-hoc techniques for mitigating their potential negative influence on
%% natural language processing. This procedure allowed us to reduce the
%% total OOV rate by ... \% for \texttt{hunspell} and by ... \% for
%% \texttt{TreeTagger}.

%% Nevertheless, we should honestly admit that our system still has
%% potential for development and research, since it mainly addresses only
%% one of three main groups of OOV tokens. Future directions should
%% certainly include a more thorough tackling of unintentional spelling
%% mistakes and especially their most prominent types -- deletions and
%% substitutions.

%% Furthemore, a better evalution technique as well as comparison with
%% other systems are needed for our normalization procedure. On the one
%% hand, an \textit{extrinsic} evaluation should be performed (cf. Sparck
%% Jones and Galliers, \cite{sparck}) which means that we not only have
%% to show how the rate of OOV words goes down but much more how this
%% lower OOV rate affects the work of the whole NLP system. On the other
%% hand, we need to assess the quality of our procedure's work on the
%% basis of metrics used by other researchers.

%% One possible estimation criterion which was used by Aw et
%% al. (\cite{aw}), Kaufmann (\cite{kaufmann}), Beaufort et
%% al. (\cite{beaufort}), and Oliva et al. (\cite{oliva}) is the BLEU
%% score (Papineni et al., \cite{papineni}). Another possibility would be
%% to use the Word (WER) and Sentence Error Rates (SER) as suggested by
%% Kobus et al. (\cite{kobus}). However, an obvious difficulty that we
%% already encountered here is that both metrics highly rely on a
%% subjective notion of the look of a ``normalized'' message. While the
%% BLEU score could be an approriate criterion for normalization of
%% messages like ``i luv ma mather and wd do evrythin 4 her'' which in
%% fact looks like as if it were not English. But such highly distorted
%% tweets are rather atypical for German. In this regard, WER and SER
%% could be considered as more appropriate measurement criteria. But
%% these metrics once again are rather dealing with spelling mistakes and
%% would highly depend on whether one, for example, would consider the
%% hash sign in a hashtag as an error.
